# Executive Summary {-}

```{r summary-setup, echo=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, cache=FALSE)
read_chunk('code/visit.R')
read_chunk('code/info.R')
```

```{r visit, include = FALSE}
```

```{r info-source, include = FALSE}
```
This report describes the results of a visitor survey at `r paste(params$RefugeName)` (this refuge). Visitors were contacted during two sampling periods outlined in Appendix A. A total of `r length(nvs2018)` visitor groups were contacted to participate in the survey. Of those groups, `r length(nvs2018)` agreed to participate in the study. Questionnaires were completed and returned by `r length(nvs2018)` visitors, resulting in a completion rate of `r length(nvs2018)/length(nvs2018)`% among those visitor groups that agreed to participate in the study and an overall response rate of `r length(nvs2018)/length(nvs2018)`% for the study.

**Key Findings:**

  - X are the most popular activities. They are also the most commonly mentioned primary reason for visiting.
  - `r (refTwo)`% respondents had visited the refuge before
  - Visitors average `r` visits per year
  - Visit length averages `r` hours
  - **The most frequently used information resource is `r tolower((infoTable$Item)[1])` (`r (infoTable$high)[1]`%).** Other frequently used information sources are `r (infoTable$Item)[2]` (`r (infoTable$high)[2]`%) and `r (infoTable$Item)[3]` (`r (infoTable$high)[3]`%). More than `r` (`r`%) did not obtain any outside information prior to visiting. 
  - Visitors opinions about this refuge
  - Transportation at this refuge
  - Visitor spending in the local communities
  - Enhancing future refuge visits
