# Visitor and Trip Characteristics {#visit}
```{r visit-setup, echo = FALSE}
library(knitr)
read_chunk('code/visit.R')
```

```{r visit, include = FALSE}
```

Data collected as part of this survey provides a baseline from which to understand who currently visits the refuge, and who engages in the multitude of activities offered by the refuge. Baseline data also allow refuge staff and others to assess any potential changes in visitor characteristics over time, which is core to the scientific foundation of the Service's Inventory and Monitoring Initiative [@USFWS2017].

## Visitor Characteristics 
```{block2, visitor-char, type='preamble1', echo=TRUE}
In particular, depictions of the demographics (e.g., age, economic status, education, race and ethnicity) of both local and non-local visitors can inform refuge managers about which groups of people are directly benefitting from what the refuge currently offers. This type of visitor data can then be compared with future visitor data to assess changes in visitation due to various conditions (e.g., shifts in climate, resource, staff, or infrastructure). Visitor demographics can also be compared to the demographic composition of nearby communities using data from U.S. Census, the American Community Survey, or through online tools such as Social Explorer (www.socialexplorer.com) to assess whether the nearby community composition is reflected within refuge visitation, which is a critical component of getting to know and relate to the community [@USFWS2014]. Such data can also determine what new audiences from the local community - if not currently reflected in the visitor population - could potentially be engaged through appropriately-targeted outreach efforts (e.g., building partnerships, enhancing stepping stones of engagement; [@USFWS2014]).
```

Visitors to `r paste(params$RefugeName)` were `r propMale`% male (with an average age of `r maleAveAge` years) and `r propFemale`% female (with an average age of `r femAveAge` years). Visitors, on average, reported they had `r (educ)` years of formal education (equivalent to `r (educLevel)`). The median level of income was `r (incLevel)`. See (AppendixB) for more demographic information. 

## Participation in Outdoor Activities
```{block2, trip-char, type='preamble1', echo=TRUE}
Quality recreational experiences on refuges provide opportunities for visitors to connect with nature and the outdoors. Specifically, wildlife-dependent recreation, such as hunting, fishing, wildlife observation or photography, environmental education, and interpretation, can increase visitor appreciation and knowledge of natural resources [@USFWS2011]. The survey collected data on recreation participation at this refuge during the past 12 months and the primary activity of each visitor when they were contacted about the survey. Understanding recreation participation can help to guide the allocation of resources, including staff and infrastructure, to ensure visitors have quality, memorable experiences. Understanding visitor uses of the refuge can also aid in developing programs that facilitate meaningful interactions between visitors and refuge staff. Finally, such information can also help to pinpoint locations on the refuge where potential interactions over refuge uses may be perceived as incompatible by different visitor groups. Anticipating and preventing any social conflicts over refuge use can help create a quality experience and foster personal and emotional connections to the refuge and its resources [@USFWS2011].

```

Refuge visitors were asked about twenty different activities they may have participated in at this refuge during the 12 months prior to completing the survey as well as the primary activity they participated in during this visit. Frequencies of all twenty activities are included in (AppendixB).

- `r (act12Table$Item)[1]` (`r (act12Table$high)[1]`%)
- `r (act12Table$Item)[2]` (`r (act12Table$high)[2]`%)
- `r (act12Table$Item)[3]` (`r (act12Table$high)[3]`%)

Refuge visitors were also given the opportunity to write-in other activities if they were not included in the list of twenty activities. The full list of ‘other reported activities are included in (AppendixC). Some of the unique activities reported at this refuge included:

- `r (act12Table$Item)[1]` (`r (act12Table$high)[1]`%)
- `r (act12Table$Item)[2]` (`r (act12Table$high)[2]`%)
- `r (act12Table$Item)[3]` (`r (act12Table$high)[3]`%)

### Primary Activities
The primary activities reported at this refuge included:

- `r (primactProp$primact)[1]` (`r (primactProp$Freq)[1]`%)
- `r (primactProp$primact)[2]` (`r (primactProp$Freq)[2]`%)
- `r (primactProp$primact)[3]` (`r (primactProp$Freq)[3]`%)


## Visiting This Refuge
```{block2, visit-char, type='preamble1', echo=TRUE}
Understanding trends in overall visitation to this refuge provides refuge staff with key information about its existing audiences. Specifically, the survey explored the number of times visitors have been to this refuge during the past year, including during which seasons, and the trips taken to other refuges or other public lands for the same primary activities. In combination with other trip characteristics (e.g., trip purpose, time spent traveling to and visiting the refuge), such information can be used to better understand activity and site fidelity (i.e., likelihood of repeating specific past behavior) or substitutability (i.e., likelihood of doing another activity or visiting somewhere else to participate in a preferred activity). Such information regarding site fidelity in particular can also help to identify the success of existing communications at enticing different groups of people to visit the refuge. Information on seasonality of visits can help refuge staff anticipate when certain recreational activities or programming is in high demand, an important informational need for allocating appropriate resources.
```

Some of the key questions related to visitation habits to this refuge included:

- Which of the following best describes your most recent visit to this refuge? 
- How many people were in your personal group, including yourself, on your most recent visit to this refuge?
- Approximately how many hours/minutes (one-way) did you travel from your home to this refuge?

### Visits to refuge
In the last 12 months, how many times have you visited this refuge (including this visit)?

- `r (refOne)`% of visitors visited the refuge only once in the last 12 months
- `r (refTwo)`% of visitors visited the refuge two times in the last 12 months

### Visits to other national wildlife refuges
In the last 12 months, how many times have you visited other national wildlife refuges?

- `r (nwrZero)`% of visitors did not visit any other national wildlife refuges in the last 12 months
- `r (nwrOne)`% of visitors visited other national wildlife refuges only once in the last 12 months
- `r (nwrTwo)`% of visitors visited other national wildlife refuges two times in the last 12 months

### Visits to other public lands
In the last 12 months, how many times have you visited other public lands (for example, national or state parks) to participate in the same primary activity as this visit?

- `r (othZero)`% of visitors did not visit any other public lands
- `r (othOne)`% of visitors visited other public lands only once
- `r (othTwo)`% of visitors visited other public lands two times


