# Communicating Refuge Information {#comm}
```{r info-setup, echo = FALSE}
library(knitr)
read_chunk('code/info.R')
```

```{r info-source, include = FALSE}
```

```{block2, type='preamble1', echo = TRUE}
Effective communication with the public is critical for managing and enhancing visitor experiences. Additionally, the Refuge System’s success in reaching new and diverse audiences depends on its ability to keep pace with communication trends [@USFWS2016a]. Understanding how visitors both seek out and share information about the refuge and its resources using various communication channels (e.g., printed information, friends and family, websites, social media) can inform the refuge's approach to communicating with visitors at different points of their trips (before, during and after). Information in this section can be used to assess changes in what sources are used as well as how visitors perceive the helpfulness of Service communications over time. Refuge staff can use communication channels preferred by visitors to inform the public about the Refuge System's mission and accomplishments. 
```

## Learning about This Refuge
The survey asked which information sources visitors used to learn about the refuge and its resources and the degree to which each information source was helpful. Visitors across different ages may use different information sources to learn about this refuge and its resources. The full list of information sources presented to visitors is contained in (AppendixB).

- Print
- Digital


## Helpfulness of Information Sources

Among all visitors, the following information sources were most frequently rated as very or extremely helpful:

- `r (infoTable$Item)[1]` (`r (infoTable$high)[1]`%)
- `r (infoTable$Item)[2]` (`r (infoTable$high)[2]`%)
- `r (infoTable$Item)[3]` (`r (infoTable$high)[3]`%)

Visitors under the age of 35 most often used these information sources to learn about the refuge:
```{r info18to34, include = FALSE}
```
- `r (infoTable18$Item)[1]` (`r (infoTable18$high)[1]`%)
- `r (infoTable18$Item)[2]` (`r (infoTable18$high)[2]`%)
- `r (infoTable18$Item)[3]` (`r (infoTable18$high)[3]`%)

Visitors over the age of 35 most often used these information sources to learn about the refuge:
```{r info35plus, include = FALSE}
```
- `r (infoTable35plus$Item)[1]` (`r (infoTable35plus$high)[1]`%)
- `r (infoTable35plus$Item)[2]` (`r (infoTable35plus$high)[2]`%)
- `r (infoTable35plus$Item)[3]` (`r (infoTable35plus$high)[3]`%)

