# Visitor Opinions about this Refuge {#opin}
```{r satisf-setup, echo = FALSE}
library(knitr)
read_chunk('code/satisfaction.R')
read_chunk('code/opportunities.R')
read_chunk('code/ImpSat.R')
read_chunk('code/safewelcome.R')

```

```{r satisfaction, include = FALSE}
```

```{block2, type='preamble1', echo=TRUE}
A baseline understanding of visitor experiences provides a framework from which the Refuge System can monitor trends in visitor experiences and opinions overtime. Obtaining such a baseline is integral to the Service's Inventory and Monitoring Initiative [@USFWS2017], as well as warranted if the Service is to remain relevant in the face of changing demographics and wildlife-related interests [@USFWS2014]. As part of the survey, visitors rated both the importance of different serv, facilities, and opportunities on the refuge, and their satisfaction with each of the things applicable to their refuge experience. Certain services or recreational opportunities may be more or less central to the experience of different segments of the visitor population, and the potential for highly varied importance ratings needs to be considered when viewing the satisfaction results of this analysis. For example, hunters may place more importance on hunting opportunities and amenities, while school-group leaders may place more importance on educational/informational displays. Thus, a specialized user group's importance of and satisfaction with a particular attribute may differ from the overall importance of and satisfaction with that same attribute for the full sample of visitors summarized in this report. 
```

## Overall Satisfaction

The vast majority of surveyed visitors were satisfied with the refuge’s job of conserving fish, wildlife, and their habitats (`r conservSat`%) and the quality of the overall experience when visiting this refuge (`r qualSat`%). The next step is to compare the importance and satisfaction ratings for visitor services provided by refuges in order to identify how well different services meet visitor expectations. 

refSatTitle
```{r echo=FALSE}
#plot(refSat)
```

## Recreational Opportunities
```{r recopps, include = FALSE}
```

### Importance of Recreational Opportunities
```{r recImp, echo=FALSE, fig.cap=recImpTitle}
plot(recImp, centered=TRUE)
```

### Satisfaction with Recreational Opportunities
```{r recSat, echo=FALSE, fig.cap=recSatTitle}
plot(recSat, centered=TRUE)
```

## Services and Facilities
```{r facserv, include = FALSE}
```

### Importance of Facilities and Services
servicesImpTitle
```{r servicesImp, echo=FALSE, fig.cap=servicesImpTitle}
plot(servicesImp, centered=TRUE)
```

### Satisfaction with Facilities and Services
servSatTitle
```{r servSatPlot, echo=FALSE, fig.cap=servicesSatTitle}
plot(servicesSat, centered=TRUE)
```

## Feeling Safe and Welcome
```{block2, type='preamble1', echo=TRUE}
People who rarely participate in wildlife-dependent recreation or do not regularly visit refuges may have different perspectives on the role of a refuge and its resources in everyday life compared to people who regularly visit a refuge or frequently participate in wildlife-dependent recreation. Visitors, particularly those new to 'being in nature', may have a sense of danger when outdoors or general discomfort associated with the unknown [@USFWS2014]. Additionally, some people may perceive the refuge to lack materials or programs accessible and relevant to their interests, or may even believe that natural places are unwelcoming because of historical associations with the outdoors. Thus, an understanding of how visitors rate their feelings of being safe and welcome on the refuge can provide important baseline information to refuge staff when identifying potential areas for improvement and evaluating how future efforts may enhance feelings of being safe and welcome at refuges over time. 
```

```{r safe, include=FALSE}
```

safeTitle
```{r echo=FALSE}
plot(safe, centered=TRUE)
```

