# Travel, Transportation and Access{-#transportation}

```{r trans-setup, echo = FALSE}
library(knitr)
read_chunk('code/AltTrans.R')
read_chunk('code/transMode.R')
read_chunk('code/transportation.R')
```

```{block2, type='preamble1', echo=TRUE}
Transportation networks connect local communities to refuges and are the bedrock of all experiences that occur on refuges. Visitors access refuges by car, by boat, by bike, and by plane. The Service works to ensure that the roads, trails and parking areas are welcoming and safe for visitors of all abilities.These networks include roads, bridges, foot pathways, entrances, and the entire suite of transportation features critical to visitor access and mobility. While many visitors arrive at the refuge in private vehicles, other options (including buses, trams, watercraft, and bicycles) are increasingly becoming a part of the visitor experience. Thus, there is a critical need to know how visitors perceive the safety of using these different transportation options, as well as different transportation features (e.g., bridges, roadways, entrances/exists) as part of their experience. The survey asked visitors to rate both the importance and current satisfaction with existing transportation-related features, as well as methods of transportation visitors used to get to and around the refuge during their visit. This information can help to identify if transportation improvements could be made that would further enhance visitor access and, ultimately, their overall experiences [@USFWS2011]. Additionally, transportation alternatives within the Refuge System [@krechmer2001; @volpe2010] could help to improve refuge conditions (e.g., quality of air, water, and habitat); thus, the survey asked visitors to note different transportation methods used during their trips, and their likelihood of using alternative transportation at refuges in the future.
```

## Travel To and On Refuge{-}
```{r transMode, include = FALSE}
```
The key mode of transportation used by visitors to travel to this refuge was `r (transModeLocalTable$Item)[1]` (`r (transModeLocalTable$high)[1]`%; fig. 11). The key mode of transportation used by visitors to travel around this refuge was `r (transModeRefTable$Item)[1]` (`r (transModeRefTable$high)[1]`%).

**Figure 11.** Modes of transportation used by visitors to travel to and around `r paste(params$RefugeName)` during this visit (*n* = `r length(transMode)`). See Appendix C for a listing of &quot;other&quot; modes of transportation. Modes of transportation with a proportion smaller than 1.5% for both items were excluded; see Appendix B for frequencies of all items.

## Transportation-related Features{-}

```{r transEval, include = FALSE}
```

A majority of visitors to `r paste(params$RefugeName)` thought transportation-related items were important. They were most satisfied with x and least satisfied with y.








•	Average travel to this refuge is [AVG#hours/minutes] for local visitors and [AVG#hours/minutes] for nonlocal visitors, with most nonlocal visitors coming from [STATE1st] [#%], [STATE2ND] [#%], AND [STATE3RD] [#%]. QUESTION: ARE PERCENTS TYPICALLY HIGH ENOUGH TO LIST THREE?
•	Visitors primarily used [MODE1ST] [#%] and [MODE2nd] [#%] to travel to the refuge
•	Once on the refuge, visits primarily used [MODE1st] [#%] and [MODE2nd] [#%]

VISUALS
WHERE VISITORS TRAVEL FROM
https://www.r-graph-gallery.com/connection-map/
https://www.r-graph-gallery.com/chloropleth-map/ 

MODES OF TRANSPORTATION
BAR CHART SHOWING “TO REFUGE” AND “ON REFUGE” FOR TOP 5 OR POSSIBLY FOR ALL (NO “OTHER”) 
Satisfaction with Transportation Safety and Ease of Access
MAY MOVE SOME THINGS IN THIS SECTION

BULLETS: 
Visitors are satisfied with transportation safety and access as follows:
•	Getting to the refuge, [#%] satisfied with directional signs on highways, {#%] satisfied with safety of entrances and exits, and [#%} satisfied with condition of roadway bridges (QUESTION IS THIS OFF OR ON REFUGE??)
•	Getting around the refuge, [#%] satisfied with …. List all 6
•	Access for recreation, [#%] satisfied with …. List all 5
•	This refuge may have room for improvement on x, y z (this would only be included if not at all, slightly and moderately are >25???% . CAN WE AUTOMATE THIS?

VISUALS

### Off refuge/getting to refuge
- Signs on highways directing you to this refuge
- Safety of refuge road entrances and exists
- Condition of Bridges on roadways

```{r trans-sat, echo=FALSE, fig.cap=transSatTitle}
plot(transSat, centered=TRUE)
```

### Getting around refuge
- Condition of Refuge Roads
- Signs directing you around on refuge
- Safety of driving condition
- Number of places to pull over on refuge
- Condition of Refuge parking areas
- Number of parking spots

### Access for recreation
- Condition of trails and boardwalks
- Safety of trails/roads for nonmotorized users
- Signs directing you on trails
- Access for people with disabilities or difficulty walking
- Condition of boat launches

## Alternative Transportation Options{-}
```{r altTrans, include = FALSE}
```
One goal of the Transportation Program is to provide alternative modes and means of access to FWS managed lands as a way to enhance the visitation experience. "Access to FWS managed lands, where compatible with Station purpose, should be available to visitors via multiple forms of transportation, including public transit, bicycle, and walking. Alternative forms of transportation can help reduce visitors' carbon footprints, which in turn may have long term positive affects for the natural resources we manage. Planning and building to accommodate sustainable transportation options can help to achieve the FWS mission [@USFWS2016b].

Of six alternative transportation options listed on the survey, a majority of refuge visitors were likely to use the following at `r paste(params$RefugeName)` in the future Figure \@ref(fig:alt-trans):

- `r (altTransTable$Item)[1]` (`r (altTransTable$high)[1]`%)
- `r (altTransTable$Item)[2]` (`r (altTransTable$high)[2]`%)
- `r (altTransTable$Item)[3]` (`r (altTransTable$high)[3]`%)

A majority of visitors indicated they were not likely to use `r (altTransTable$Item)[6]`.

```{r alt-trans, echo=FALSE, fig.cap=altTransTitle}
plot(altTrans, centered=TRUE)
```
