# Visitor Spending in the Local Communities{-#spending}

```{r econ-setup, echo = FALSE}
library(knitr)
#nvs2018 <- readr::read_csv("data/nvs2018.csv")
read_chunk('code/econ.R')
read_chunk('code/spending.R')
```

```{r spending, include = FALSE}
```

```{block2, econ-preamble, type='preamble1', echo=TRUE}
Tourists tend to buy a range of goods and services while visiting an area, such as a city or town located adjacent to a refuge. Major expenditure categories include lodging, food, supplies, and gasoline. Spending associated with refuge visitation can generate considerable economic benefits for local communities. For example, more than 46.5 million visits were made to refuges in fiscal year 2011, and generated $2.4 billion in sales, more than 35,000 jobs, and $792.7 million in employment income in regional economies [@carver2013]. Information on the amount and types of visitor expenditures in relation to particular recreation activities (e.g., hunting, fishing, wildlife observation) has further illustrated the economic importance of recreation [@USFWS2018], which are the primary reasons for which visitors seek out refuges and related resources. Finally, visitor expenditure information can be used to determine the potential economic impact of proposed refuge management alternatives into the future.
```

## Visitor Spending in the Local Communities{-}
Visitors that live within the local 50-mile area of a refuge typically have different spending patterns than those that travel from longer distances. During the two sampling periods, `r (propLocal)`% of surveyed visitors to `r paste(params$RefugeName)` indicated that they live within the local 50-mi area while nonlocal visitors (`r (propNonlocal)`%) stayed in the local area, on average, for `r mean(timeLocal)` days. (tab:expendTable) shows summary statistics for local and nonlocal visitor expenditures in the local communities and at the refuge, with expenditures reported on a per person per day basis. During the two sampling periods, nonlocal visitors (_n_ = `r (propNonlocal)`) spent an average of $`r round_df(mean(spendNonloc$TOTALpersonday),2)` per person per day and local visitors spent an average of $`r round_df(mean(spendLocal$TOTALpersonday),2)` per person per day in the local area. It is important to note that summary statistics based on a small sample size (n < 30) may not provide a reliable representation of that population. Several factors should be considered when estimating the economic importance of refuge-visitor spending in the local communities. These factors include the amount of time spent at the refuge, influence of the refuge on the visitors’ decision to take this trip, and the representativeness of primary activities of the sample of surveyed visitors compared to the general population. Controlling for these factors is beyond the scope of the summary statistics presented in this report.

Visitors to this refuge can be characterized as follows: 

- [#%] of visitors are from the local area (<50 miles) and [#%]  live beyond the local areas
- Nonlocal visits spend [#days/hours] on average in the local community
- Visitors spend and average of [$#] per person per day in the local community on such amenities as lodging, food, and supplies, with local visitors averaging [$#] and nonlocal visitors averaging [$#]


Table: (\#tab:spend-table)
```{r echo=FALSE, tab.cap="Total visitor expenditures in local communities and at `r paste(params$RefugeName)` expressed in dollars per person per day"}
kable(spendTable,
      digits = c(0, 0, 2, 2, 2, 2, 2),
      align = "lcrrrrr") %>%
  kable_styling(full_width = FALSE, position = "left") %>%
  footnote(
    footnote_order = c("number", "general"),
    number = c(
      "n = number of visitors who answered both locality and expenditure questions."
    ),
    general = "For each respondent, reported expenditures were divided by the number of persons in their group that shared expenses in order to determine the spending per person per trip. This number was then divided by the number of days spent in the local area to determine the spending per person per day for each respondent. For respondents who reported spending less than one full day in the local community, trip length was set equal to one day. These visitor spending estimates are appropriate for the sampling periods selected by refuge staff (see [Table] for sampling period dates and (fig:primactFig) for the primary visitor activities in which people participated), and may not be representative of the total population of visitors to this refuge."
  )
```

```{r echo=FALSE, fig.cap="Total visitor expenditures in local communities and at `r paste(params$RefugeName)` expressed in dollars per person per day"}
spendPlot + theme_fivethirtyeight() + 
  scale_fill_brewer(palette = "Spectral")
```


