# Appendix B: Survey Frequencies for `r params$RefugeName` {-#AppendixB}
```{r appendB, echo = FALSE}
library(knitr)
read_chunk('code/satisfaction.R')
read_chunk('code/opportunities.R')
read_chunk('code/ImpSat.R')
read_chunk('code/safewelcome.R')

```

## Overall Satisfaction{-}

```{r echo=FALSE}
#plot(refSat)
```

## Recreational Opportunities{-}
```{r recopps, include = FALSE}
```

### Importance of Recreational Opportunities{-}
```{r recImp, echo=FALSE, fig.cap=recImpTitle}
plot(recImp, centered=TRUE)
```

### Satisfaction with Recreational Opportunities{-}
```{r recSat, echo=FALSE, fig.cap=recSatTitle}
plot(recSat, centered=TRUE)
```

## Services and Facilities{-}
```{r facserv, include = FALSE}
```

Positive experiences are driven by first impressions of refuge facilities and people.

### Importance of Facilities and Services{-}
servicesImpTitle
```{r servicesImp, echo=FALSE, fig.cap=servicesImpTitle}
plot(servicesImp, centered=TRUE)
```

### Satisfaction with Facilities and Services{-}
```{r servSatPlot, echo=FALSE, fig.cap=servicesSatTitle}
plot(servicesSat, centered=TRUE)
```

## Feeling Safe and Welcome{-}

```{r safe, include=FALSE}
```

safeTitle
```{r echo=FALSE}
plot(safe, centered=TRUE)
```

