```{r sm-setup, echo = FALSE}
library(knitr)
read_chunk('code/socialMedia.R')
```

```{r socmedia, include = FALSE}
```

# Sharing Refuge Experiences Via Social Media {#smed}
```{block2, type='preamble1', echo=TRUE}
Around 70% of Americans use social media to connect with one another, engage with news content, share information and entertain themselves [@smith2018]. Understanding the role of social media can expand the reach of Service communication efforts and direct ways to better reach the next generation of refuge visitors, a major emphasis of the Service's recommendations for Conserving the Future [@USFWS2011]. Building and maintaining an official presence on social media can also enhance two-way conversations between visitors and refuge staff, a critical element of the Service's Communication's Strategy [@USFWS2016a]. Two-way communication may also help to enhance trust of the agency by highlighting the range of visitor experiences that are welcomed and stories of refuges experiences from the perspective of culturally-relevant groups [@USFWS2014]. Finally, a social media presence can further generate awareness of the refuge and its resources among audiences that do not use, or did not otherwise learn about the refuge through traditional advertising outlets.

In an increasingly urbanized society, social media is how a lot of younger generations are getting introduced to outdoor spaces for the first time.
```

Visitors were asked if they used social media to share their refuge experience with others. Potential visitors may find these shared posts when searching for information online about the refuge, specific locations, or particular wildlife - or simply when searching about their friend or family member's activities; thus, social media posts can serve as a virtual "word of mouth" method of increasing awareness about the refuge to the visitor's network and beyond. 

`r if(useSocmed <48){"Less than "}else if(useSocmed >= 48 & useSocmed <= 52){"About "}else if(useSocmed > 52){"More than "}` half of visitors (`r useSocmed`%) reported using social media to share their refuge experience with other people. The full list of social media outlets presented to visitors is contained in Appendix B.

### Social Media Sharing by Age Group{-}
While Millennials have often led older Americans in their adoption and use of technology, including social media, there has been significant growth in tech adoption in recent years among older generations. More than half of Baby Boomers say they use social media [@smith2018]. Among all visitors, the following social media outlets were used most often to share refuge experiences:

- `r (smTable$Item)[1]` (`r (smTable$high)[1]`%)
- `r (smTable$Item)[2]` (`r (smTable$high)[2]`%)
- `r (smTable$Item)[3]` (`r (smTable$high)[3]`%)

<table border="0">
 <tr>
    <td>
    Visitors under the age of 35 most often used these social media outlets to share refuge experiences:

- `r (smTable18to34$Item)[1]` (`r (smTable18to34$high)[1]`%)
- `r (smTable18to34$Item)[2]` (`r (smTable18to34$high)[2]`%)
- `r (smTable18to34$Item)[3]` (`r (smTable18to34$high)[3]`%)
</td>
  </tr>
 <tr>
   <td>
Visitors over the age of 35 most often used these social media outlets to share refuge experiences:

- `r (smTable$Item)[1]` (`r (smTable$high)[1]`%)
- `r (smTable$Item)[2]` (`r (smTable$high)[2]`%)
- `r (smTable$Item)[3]` (`r (smTable$high)[3]`%)
    </td>
 </tr>
</table>

